<p align = right> Shivani Mankotia : sxm180018</p>
<p align = right> Prateek Sarna : pxs180012</p>
<center><h2>ETHEREUM DATASET</h2>
<h4>Project 1 : Statistical Methods for Data Science</h4> 
<h4>Token: BNB</h4> </center>

```{r}

library(anytime)

tokenBNB <- read.table("networkbnbTX.txt", sep = " ", header = TRUE)
colnames(tokenBNB) <- c("FromNodeID","ToNodeID","Date","TokenAmount")
#tokenBNB$Date <- format(as.Date(tokenBNB$Date, format = "%m/%d/%Y"), "%Y-%m-%d")
tokenBNB$Date <- anydate(tokenBNB$Date)
head(tokenBNB)

#tokenPrices <- read.csv("bnb_all_time.csv")
tokenPrices <- read.table("bnb.txt", sep = "\t", header = TRUE)
colnames(tokenPrices) <- c("Date",	"Open",	"High",	"Low", "Close",	"Volume",	"Market Cap")
tokenPrices$Date <- format(as.Date(tokenPrices$Date, format = "%m/%d/%Y"), "%Y-%m-%d")
tokenPrices$Date <- anydate(tokenPrices$Date)
#tokenPrices$Date <- as.Date(as.POSIXct(tokenPrices$Date, origin="1970-01-01"))
head(tokenPrices)
```

```{r}
#Frequency Vs TokenAmount
library(dplyr)
df <- tokenBNB %>%
  group_by(TokenAmount) %>%
  summarize(counts = n())

df
#Plot of the entire data
plot(df)
```
<p>We constructed layers based on how concentrated the data was. In this chunk of code, we plotted Frequency vs TokenAmount graph which gave us visual estimation of the same.</p>
```{r}

#TEST LAYERS
#layer1 <- token[which(token$TokenAmount > 5e+24 & token$TokenAmount <= 2e+25), ]
#layer2 <- token[which(token$TokenAmount > 2e+24 & token$TokenAmount <= 5e+24),]
#layer3 <- token[which(token$TokenAmount > 1e+24 & token$TokenAmount <= 2e+24),]
#layer4 <- token[which(token$TokenAmount > 8e+23 & token$TokenAmount <= 1e+24),]
#layer5 <- token[which(token$TokenAmount > 4e+23 & token$TokenAmount <= 8e+23),]
#layer6 <- token[which(token$TokenAmount > 3e+23 & token$TokenAmount <= 4e+23),]
#layer7 <- token[which(token$TokenAmount > 2.5e+23 & token$TokenAmount <= 3e+23),]
#layer8 <- token[which(token$TokenAmount > 2e+23 & token$TokenAmount <= 2.5e+23),]
#layer9 <- token[which(token$TokenAmount > 1.5e+23 & token$TokenAmount <= 2e+23),]
#layer10 <- token[which(token$TokenAmount > 1e+23 & token$TokenAmount <= 1.5e+23),]
#layer11 <- token[which(token$TokenAmount > 8e+22 & token$TokenAmount <= 1e+23),]
#layer12 <- token[which(token$TokenAmount > 7e+22 & token$TokenAmount <= 8e+22),]
#layer13 <- token[which(token$TokenAmount > 6e+22 & token$TokenAmount <= 7e+22),]
#layer14 <- token[which(token$TokenAmount > 5.5e+22 & token$TokenAmount <= 6e+22),]
#layer15 <- token[which(token$TokenAmount > 5e+22 & token$TokenAmount <= 5.5e+22),]
#layer16 <- token[which(token$TokenAmount > 4.5e+22 & token$TokenAmount <= 5e+22),]
#layer17 <- token[which(token$TokenAmount > 4e+22 & token$TokenAmount <= 4.5e+22),]
#layer18 <- token[which(token$TokenAmount > 3.5e+22 & token$TokenAmount <= 4e+22),]
#layer19 <- token[which(token$TokenAmount > 3e+22 & token$TokenAmount <= 3.5e+22),]
#layer20 <- token[which(token$TokenAmount > 2.75e+22 & token$TokenAmount <= 3e+22),]
#layer21 <- token[which(token$TokenAmount > 2.5e+22 & token$TokenAmount <= 2.75e+22),]
#layer22 <- token[which(token$TokenAmount > 2.25e+22 & token$TokenAmount <= 2.5e+22),]
#layer23 <- token[which(token$TokenAmount > 2e+22 & token$TokenAmount <= 2.25e+22),]
# Layers 24 - 28 have the most concentrated data points. 
#layer24 <- token[which(token$TokenAmount > 1.5e+22 & token$TokenAmount <= 2e+22), ] 
#layer25 <- token[which(token$TokenAmount > 1.0e+22 & token$TokenAmount <= 1.5e+22), ]
#layer26 <- token[which(token$TokenAmount > 5.0e+21 & token$TokenAmount <= 1.0e+22), ]
#layer27 <- token[which(token$TokenAmount > 1.0e+22 & token$TokenAmount <= 1.5e+22), ]
#layer28 <- token[which(token$TokenAmount > 0 & token$TokenAmount <= 5.0e+21), ]



#Chosen layer for testing the co-relation coefficients. 
layer<- tokenBNB[which(tokenBNB$TokenAmount>1e+18 & tokenBNB$TokenAmount<=1e+21),]
df2 <-layer %>%
  group_by(TokenAmount) %>%
  summarize(counts = n())
#Plot of the chosen layer
df2 <- df2[df2$counts <= 400, ]
head(df2)
plot(df2)

```
```{r}

# df3 <- data.frame(table(layer$TokenAmount))
# colnames(df3) <- c("TokenAmount", "Count")
# #df3 <- df3[df3$Count <= 400, ]
# head(df3)
# plot(df3)

```


By visual observation, this layer has the maximun concentration of data. 

```{r}
library(ggplot2)

layerDate <-c(layer[,3])
count_layerDate<-as.data.frame(table(layerDate))
colnames(count_layerDate)<-c("Date","Frequency")
count_layerDate$Date <- as.Date(anydate(count_layerDate$Date))

#Joining the two tables using inner join
tableJoin <- merge(count_layerDate, tokenPrices)

df <- data.frame(tableJoin$Date, tableJoin$High, tableJoin$Frequency)
plot(x = df$tableJoin.Date, y = df$tableJoin.High)
#ggplot(data = df, aes(x = df$tableJoin.Date, y = df$tableJoin.High))

```
<p>The above graph is a plot of Date vs Price: High. 

We tested our data on all the three Correlation Coefficients: Pearson, Spearman and Kendall. 
Below are the results with corresponding graphs:</p>

```{r}
library(ggplot2)
library(ggpubr)
#PEARSON cO-RELATION
cor.test(df$tableJoin.High, df$tableJoin.Frequency, method = "pearson")

ggscatter(df, x = "tableJoin.Date", y = "tableJoin.High", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Date", ylab = "Price(High)")

#SPEARMAN CO-RELATION
cor.test(df$tableJoin.High, df$tableJoin.Frequency, method = "spearman")

ggscatter(df, x = "tableJoin.Date", y = "tableJoin.High", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "Date", ylab = "Price(High)")

#KENDALL C0-RELATION
cor.test(df$tableJoin.High, df$tableJoin.Frequency, method = "kendall")

ggscatter(df, x = "tableJoin.Date", y = "tableJoin.High", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "kendall",
          xlab = "Date", ylab = "Price(High)")

```
<p><b> Conclusion: </b>
According to above results, the Spearman Correlation gives us the highest coefficent value. 

The following are the results obatined:<br> 
Pearson : cor 0.5030097<br>
Spearman: rho 0.7264976<br>
Kendall: tau 0.5234409</p>




