
<p align = right> Shivani Mankotia : sxm180018</p>
<p align = right> Prateek Sarna : pxs180012</p>
<center><h2>ETHEREUM DATASET</h2>
<h4>Project 1 : Statistical Methods for Data Science</h4> 
<h4>Token: BNB</h4> </center>

```{r}
#TOKEN NAME: BNB
#Total Supply: $1,978,317,006.32
#Decimals:18

token <- read.table("networkbnbTX.txt", sep =" ", header = FALSE)
colnames(token) <- c("FromNodeID","ToNodeID","Time","TokenAmount")

#displaying 20 random rows out of almost 36 thousand rows
token[sample(nrow(token), 20),]

# Removing Outliers for BNB 
total_supply = 1978317006.32
decimals = 1000000000000000000
outliers <- token[(token$TokenAmount > (total_supply * decimals)), ]
#There are no outlier amounts
outliers

#Updating token table: Removing outliers (if any)
token_updated <- token[!(token$TokenAmount > (total_supply * decimals)), ]
#displaying 20 random rows out of almost 36 thousand rows
token_updated[sample(nrow(token_updated), 20),]
```



```{r}
library(plyr)
#FOR SELLING TOKENS
count_users_sells = count(token_updated, "FromNodeID")
count_users_sells[sample(nrow(count_users_sells), 20),]

#taking frequency of freq
counts_sells <- table(count_users_sells$freq)

#taking top 10 values on x-axis 
barplot(counts_sells,xlim=c(0, 10), main="Number of times a Token was sold", 
  	xlab="Number of sells",ylab="Number of Users")

#FOR BUYING TOKENS
count_users_buys = count(token_updated, "ToNodeID")
count_users_buys[sample(nrow(count_users_buys), 20),]

#taking frequency of freq
count_buys <- table(count_users_buys$freq)

#taking top 10 values on x-axis 
barplot(count_buys,xlim=c(0, 10), main="Number of times a Token was bought", 
  	xlab="Number of buys",ylab="Number of Users")

```
<br><b>Question1:</b> Find the distribution of how many times a user 1 - buys, 2 - sells a token. Which discrete distribution type fits these distributions best? Estimate distribution parameters. 

```{r}
library(MASS)
library(fitdistrplus)

#converting frequency tables to vector form 

count_sells_vector <- as.vector(counts_sells)
count_buy_vector <- as.vector(count_buys)
```

According to our observations Poisson Distribution and Negative Binomial Distribution fit our data the best. The following are the graphs for the same: 

```{r}
library(fitdistrplus)

#Distribution Types for Selling of Tokens

cat("Mean is: " , mean(count_sells_vector), "\n") 
cat("Variance is: " , var(count_sells_vector), "\n")
cat("Standard Deviation is: " , sd(count_sells_vector), "\n")

#Negative Binomial
N.nbinom<-fitdist(count_sells_vector, distr = "nbinom")
plot(N.nbinom)
summary(N.nbinom)

#Poisson Distribution
N.pos <- fitdist(count_sells_vector, distr = "pois")
plot(N.pos)
summary(N.pos)

#Distribution Types for Buying of Tokens

cat("Mean is: " , mean(count_buy_vector), "\n") 
cat("Variance is: " , var(count_buy_vector), "\n")
cat("Standard Deviation is: " , sd(count_buy_vector), "\n")

#Negative Binomial
N.nbinom<-fitdist(count_buy_vector, distr = "nbinom")
plot(N.nbinom)
summary(N.nbinom)

#Poisson Distribution
N.pos <- fitdist(count_buy_vector, distr = "pois")
plot(N.pos)
summary(N.pos)
```
<b>Conclusion:</b>
According to above graphs, our data best fits Negative Binomial and Poisson Distributions. 

Since, varinace and mean of Poisson Distribution for both Buying and Selling of Tokens in not equal to lambda, hence Poisson will not be the appropriate fit. 

It fits Negative Binomial Distribution the best.  